\documentclass[12pt, letterpaper]{report}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=2cm]{geometry}

%% Useful packages
    %% math and units
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage{hepunits}
\DeclareSIUnit\barn{b}
\usepackage{xspace}
    %% tables and figures
\usepackage{graphicx}    
\usepackage{rotating}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{subcaption}
    %% formatting
\usepackage[indent=0pt]{parskip}
\usepackage{titlesec}
    %% cross-references
\usepackage{url}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage[nameinlink, capitalise]{cleveref}
\usepackage[numbers, sort&compress]{natbib}

%commands
\newcommand{\pt}{\ensuremath{p_\mathrm{T}}\xspace}
\newcommand{\mt}{\ensuremath{m_\mathrm{T}}\xspace}
\newcommand{\ptmiss}{\ensuremath{\pt^\text{miss}}\xspace}
\newcommand{\ptvecmiss}{\ensuremath{\vec{p}_\mathrm{T}^{\kern2pt\text{miss}}}\xspace}
\DeclareRobustCommand{\GeV}[1]{\ensuremath{\SI{#1}{\GeV}}}
\newcommand{\TeV}[1]{\SI{#1}{\TeV}}
\newcommand{\fbinv}[1]{\SI{#1}{\invfb}}
\newcommand{\Zp}{\ensuremath{{\mathrm{Z}'}}\xspace}

\newcommand{\crefrangeconjunction}{--}

\numberwithin{equation}{chapter}

\title{\textbf{Search for Dark Matter Produced in Association with a Higgs Boson Decaying to a Bottom Quark and Antiquark Pair Plus Missing Transverse Momentum at the HL-LHC}}
\author{\textbf{Jackson Wallace}}

\begin{document}
\maketitle
\tableofcontents

\titleformat{\chapter}{}{}{0em}{\bf\LARGE\thechapter.~}

\begin{abstract}
The inability to explain the phenomenon of dark matter remains one of the largest flaws with the Standard Model of particle physics.
This thesis gives an overview of current efforts to understand dark matter, with a focus on indirect searches for dark matter produced in association with a Higgs boson. 
With the higher rate of collisions at the High-Luminosity Large Hadron Collider (HL-LHC) as well as the  Phase-2 upgrade of the Compact Muon Solenoid (CMS) detector, these searches present an excellent avenue to explore the mystery of dark matter. 
This thesis then presents a projection study for the sensitivity of the upgraded CMS detector to new physics, especially dark matter, in the mono-Higgs sector, examining an h $\to$ b$\bar{\mathrm{b}}$ plus missing transverse momentum final state at the HL-LHC.
The focus lies on signals with high-momentum Higgs bosons, resulting in a large radius jet that can be identified as originating from a Higgs boson.
The search is sensitive to a variety of physics beyond the Standard Model including a two Higgs doublet model with a pseudoscalar mediator (2HDM+a). This model proposes two additional massive pseudoscalars, labeled A and a. This thesis reveals that the HL-LHC, with an expanded $\fbinv{3000}$ dataset, will have additional sensitivity to BSM physics. If observed, 2HDM+a signals with $m_\mathrm{a} = \GeV{250}$ and $m_\mathrm{A}$ from $1000$ to $\GeV{1600}$ could have a significance near 5$\sigma$ or greater.
If no significant excess is observed, the exclusion of parameters of the 2HDM+a model can be extended. Signals with $m_\mathrm{A}$ values from $750$ to $\GeV{2000}$ could be excluded for $m_\mathrm{a}$ equal to $\GeV{250}$, while signals with $m_\mathrm{A}$ from $1250$ to $\GeV{1600}$ could be excluded for $m_\mathrm{a} = \GeV{500}$. 
\end{abstract}

\input{Chapters/Intro/intro}
\input{Chapters/Theory/theory}
\input{Chapters/CMS/cms}
\input{Chapters/Experiment/experiment}
\input{Chapters/Datasets/datasets}
\input{Chapters/Strategy/strategy}
\input{Chapters/Signal_Extraction/signal_extraction}
\input{Chapters/Systematics/systematics}
\input{Chapters/Results/results}

\appendix
\input{Chapters/app_samples}

\titleformat{\chapter}{}{}{0em}{\bf\LARGE}

\clearpage
\input{Chapters/acknowledgements}

\bibliographystyle{cms_unsrt}
\clearpage
\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{hbbmet}

\end{document}
